MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
removed more code

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{hsv.png}
  \caption{The HSV color cylinder}
  \label{fig:hsv}
\end{figure}

@@

Conversion to music happens by doing operations on colors and image
data.  To do the conversion to tone, velocity pairs, we transform
colors in the input data, meaning that we have to start with a
representation of $R$ colors for each image.  To do this
transformation, we considered using a MapReduce job: mapping over the
sets of images in our input corpus.  Ultimately we found that
converting images to thumbnails was better accomplished using scripts:
which allowed us to do other manipulation as well.  We anticipate that
if this became a problem we could have moved the image processing code
to Java and pass in our input corpus to the initial stage of
MapReduce.  Our current implementation uses the RMagick \cite{rmagick}
gem, which is a Ruby library interfacing to ImageMagick
\cite{imagemagick}.  ImageMagick includes facilities for taking images
to thumbnails.

\begin{figure}
\begin{lstlisting}[language=Ruby]
require 'rmagick'

class ThumbMaker
  # Convert set of images to thumbnails
  def self.convert_thumbs(dir_path, size)
      # ... 
      puts "Making thumbnail for..."
      Dir.glob("#{path}/*.jpg") do |fname|
        # ...
        fname = # ...
        img = Magick::Image.read(fname)[0]
        thumb = img.thumbnail(size, size)
        thumb.write(thumb_dest)
      end
    end
end

\end{lstlisting}
\caption{Relevant code from the module used for image to thumbnail
  conversion}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.4\textwidth]{hsv.png}
  \caption{The HSV color cylinder}
  \label{fig:hsv}
\end{figure}

@@

Conversion to music happens by doing operations on colors and image
data.  To do the conversion to tone, velocity pairs, we transform
colors in the input data, meaning that we have to start with a
representation of $R$ colors for each image.  To do this
transformation, we considered using a MapReduce job: mapping over the
sets of images in our input corpus.  Ultimately we found that
converting images to thumbnails was better accomplished using scripts:
which allowed us to do other manipulation as well.  We anticipate that
if this became a problem we could have moved the image processing code
to Java and pass in our input corpus to the initial stage of
MapReduce.  Our current implementation uses the RMagick \cite{rmagick}
gem, which is a Ruby library interfacing to ImageMagick
\cite{imagemagick}.  ImageMagick includes facilities for taking images
to thumbnails, we simply use the RMagick library to preprocess all of
our images so that they are in the correct dimensions and are of the
proper size.

%% \begin{figure}
%% \begin{lstlisting}[language=Ruby]
%% require 'rmagick'

%% class ThumbMaker
%%   # Convert set of images to thumbnails
%%   def self.convert_thumbs(dir_path, size)
%%       # ... 
%%       puts "Making thumbnail for..."
%%       Dir.glob("#{path}/*.jpg") do |fname|
%%         # ...
%%         fname = # ...
%%         img = Magick::Image.read(fname)[0]
%%         thumb = img.thumbnail(size, size)
%%         thumb.write(thumb_dest)
%%       end
%%     end
%% end

%% \end{lstlisting}
%% \caption{Relevant code from the module used for image to thumbnail
%%   conversion}
%% \end{figure}
